### 2023-04-06 main.tex
i

    \begin{equation}\label{InverseS2}
    	\begin{split}
    		\mathcal{S}_{2}^{-1}=\left(S_{2}^{\otimes L}\right)^{-1}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}++\sum_{q_{1}=1}^{L}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\right. 
    		\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}\right.
    		\\&+\left.
    		\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{s_{q_{t}},1})\right)e_{s_{1},\ldots,s_{q_{L-1}s_{L}}}^{1,\ldots,1,s_{L}}
    		\right. \\&+ \left. 
    		\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\beta_{s_{x}}e_{s_{1},\ldots,s_{L}}^{1,\ldots,1} \right\}
    	\end{split}
    \end{equation}
    We prove it by induction. When $L=1$ it is true, indeed
    \begin{equation}
    	S_{2}^{-1}=\sum_{s_{1}=1}^{N}\left\{e_{s_{1}}^{s_{1}}+(1-\delta_{s_{1},1})\sum_{q_{1}=1}^{1}\beta_{s_{q_{1}}}e_{s_{q_{1}}}^{1}\right\}
    \end{equation}
    Assuming that \eqref{InverseS2} is true for $L$, we prove that it holds for $L+1$
\begin{align*}
    	\left(S_{2}^{\otimes L}\right)^{-1}\otimes S_{2}^{-1}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}++\sum_{q_{1}=1}^{L}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\right. 
    	\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}\right.
    	\\&+\left.
    	\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{s_{q_{t}},1})\right)e_{s_{1},\ldots,s_{q_{L-1}s_{L}}}^{1,\ldots,1,s_{L}}
    	\right. \\&+ \left. 
    	\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\beta_{s_{x}}e_{s_{1},\ldots,s_{L}}^{1,\ldots,1} \right\}\otimes \sum_{s_{L+1}=1}^{N}\left\{e_{s_{L+1}}^{s_{L+1}}+(1-\delta_{s_{L+1},1})\sum_{q_{1}=1}^{1}\beta_{s_{q_{1}}}e_{s_{q_{1}}}^{1}\right\}
    	\\&=
    	\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L+}=1}^{N}\left\{e_{s_{1},\ldots,s_{L+1}}^{s_{1},\ldots,s_{L+1}}+\sum_{q_{1}=1}^{L+1}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L+1}}^{s_{1},\ldots,1,\ldots,s_{L+1}}\beta_{s_{q_{1}}}\right. 
    	\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L+1}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L+1}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L+1}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}\right.
    	\\&+\left.
    	\ldots+	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L}(1-\delta_{s_{q_{t}},1})\right)e_{s_{1},\ldots,s_{q_{L}}s_{L+1}}^{1,\ldots,1,s_{L+1}}
    	\right. \\&+ \left. 
    	\left(\prod_{x=1}^{L+1}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L+1}\beta_{s_{x}}e_{s_{1},\ldots,s_{L+1}}^{1,\ldots,1} \right\}
    	\\&=
    	\left(S_{2}^{\otimes L+1}\right)^{-1}
\end{align*}
    \begin{comment}

@@

\paragraph{Proof of formula \eqref{steadyStateH}} As a consequence of \eqref{S1-Inverse}, we only need to show how the transformation $\mathcal{S}_{1}^{-1}$ acts on the vector $|\Psi^{'}\rangle$. The matrix $S_{2}^{-1}$, acting on a single site, is given by 
\begin{equation}\label{S1-L1}
	S_{1}^{-1}=\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}+(-1)\delta_{s_{1},1}\sum_{d_{1}=2}^{N}e_{1}^{d_{1}}
\end{equation}
Using the notation introduced in \eqref{notation1} and \eqref{notation2} we have that 
\begin{equation}
	\begin{split}
		\mathcal{S}_{1}^{-1}=\left(S_{1}^{\otimes L}\right)^{-1}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}\right.
		\\&
		+\left.\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}\right\} 
	\end{split}
\end{equation}
where $e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}$ denotes the matrix $e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}$ where the subscripts $s_{q_{1}},\ldots,s_{q_{b}}$ have been replaced by "1" and the superscripts $s_{q_{1}},\ldots,s_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$. \\
This is proved by induction. Indeed, for $L=1$ it is trivially true, by \eqref{S1-L1}. We assume that it is true for $L$ and we prove that it holds for $L+1$. 
\begin{align*}
\left(S_{1}^{\otimes L}\right)^{-1}\otimes S_{1}^{-1}&=
\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}\right. \\&+\left. \sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}\right\}
\\&\otimes
\left\{ \sum_{s_{1}=1}^{N}e_{s_{L+1}}^{s_{L+1}}+(-1)\delta_{s_{L+1},1}\sum_{d_{L+1}=2}^{N}e_{1}^{d_{L+1}}\right\}
\\&=
\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L+1}=1}^{N}\left\{e_{s_{1},\ldots,s_{L+1}}^{s_{1},\ldots,s_{L+1}}\right. \\&+\left. \sum_{b=1}^{L+1}(-1)^{b}\sum_{q_{1}=1}^{L+1}\sum_{q_{2}=q_{1}+1}^{L+1}\ldots\sum_{q_{b}=q_{b-1}+1}^{L+1}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}\right\}
\end{align*}
\begin{comment}

@@

    \mathcal{L}^{rd}=\sum_{x,y\in\mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}^{rd}+\sum_{x\in V}\Gamma_{x}\mathcal{L}_{x}

@@

	\mathcal{L}_{x}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)

@@

@@

\mathcal{L}_{x,y}^{c}n_{a}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left(n_{d}^{x}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(a)}^{y}-\delta_{b}^{y}-n_{\alpha}^{x}\right)=\sum_{a=1}^{N}n_{a}^{x}n_{q}^{y}-\sum_{\ell=1}^{N}n_{\alpha}^{x}n_{\ell}^{y}

@@

where we call $q\in \{2,\ldots,N\}$ such that $g_{i}(q)=\alpha$ and $\ell\in \{2,\ldots,N\}$ such that $g_{i}(\ell)\neq \alpha$. Summing over all indices $c\in\{2,\ldots,N\}\,:\,c\neq d$ we obtain \eqref{actionGraphRD}.\\

>>>>

    \begin{equation}\label{InverseS2}
    	\begin{split}
    		\mathcal{S}_{2}^{-1}=\left(S_{2}^{\otimes L}\right)^{-1}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}++\sum_{q_{1}=1}^{L}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\right. 
    		\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}\right.
    		\\&+\left.
    		\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{s_{q_{t}},1})\right)e_{s_{1},\ldots,s_{q_{L-1}s_{L}}}^{1,\ldots,1,s_{L}}
    		\right. \\&+ \left. 
    		\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\beta_{s_{x}}e_{s_{1},\ldots,s_{L}}^{1,\ldots,1} \right\}
    	\end{split}
    \end{equation}
    We prove it by induction. When $L=1$ it is true, indeed
    \begin{equation}
    	S_{2}^{-1}=\sum_{s_{1}=1}^{N}\left\{e_{s_{1}}^{s_{1}}+(1-\delta_{s_{1},1})\sum_{q_{1}=1}^{1}\beta_{s_{q_{1}}}e_{s_{q_{1}}}^{1}\right\}
    \end{equation}
    Assuming that \eqref{InverseS2} is true for arbitrary $L\in \mathbb{N}$, we prove that it holds for $L+1$
\begin{align*}
    	\left(S_{2}^{\otimes L}\right)^{-1}\otimes S_{2}^{-1}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}++\sum_{q_{1}=1}^{L}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\right. 
    	\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}\right.
    	\\&+\left.
    	\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{s_{q_{t}},1})\right)e_{s_{1},\ldots,s_{q_{L-1}s_{L}}}^{1,\ldots,1,s_{L}}
    	\right. \\&+ \left. 
    	\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\beta_{s_{x}}e_{s_{1},\ldots,s_{L}}^{1,\ldots,1} \right\}\otimes \sum_{s_{L+1}=1}^{N}\left\{e_{s_{L+1}}^{s_{L+1}}+(1-\delta_{s_{L+1},1})\sum_{q_{1}=1}^{1}\beta_{s_{q_{1}}}e_{s_{q_{1}}}^{1}\right\}
    	\\&=
    	\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L+}=1}^{N}\left\{e_{s_{1},\ldots,s_{L+1}}^{s_{1},\ldots,s_{L+1}}+\sum_{q_{1}=1}^{L+1}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L+1}}^{s_{1},\ldots,1,\ldots,s_{L+1}}\beta_{s_{q_{1}}}\right. 
    	\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L+1}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L+1}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L+1}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}\right.
    	\\&+\left.
    	\ldots+	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L}(1-\delta_{s_{q_{t}},1})\right)e_{s_{1},\ldots,s_{q_{L}}s_{L+1}}^{1,\ldots,1,s_{L+1}}
    	\right. \\&+ \left. 
    	\left(\prod_{x=1}^{L+1}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L+1}\beta_{s_{x}}e_{s_{1},\ldots,s_{L+1}}^{1,\ldots,1} \right\}
    	\\&=
    	\left(S_{2}^{\otimes L+1}\right)^{-1}
\end{align*}
    \begin{comment}

@@

\paragraph{Proof of formula \eqref{steadyStateH}} As a consequence of \eqref{S1-Inverse}, we only need to show how the transformation $\mathcal{S}_{1}^{-1}$ acts on the vector $|\Psi^{'}\rangle$. The matrix $S_{2}^{-1}$, acting on a single site, is given by 
\begin{equation}\label{S1-L1}
	S_{1}^{-1}=\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}+(-1)\delta_{s_{1},1}\sum_{d_{1}=2}^{N}e_{1}^{d_{1}}
\end{equation}
Using the notation introduced in \eqref{notation1} and \eqref{notation2} we have that 
\begin{equation}
	\begin{split}
		\mathcal{S}_{1}^{-1}=\left(S_{1}^{\otimes L}\right)^{-1}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}\right.
		\\&
		+\left.\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}\right\} 
	\end{split}
\end{equation}
where $e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}$ denotes the matrix $e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}$ where the subscripts $s_{q_{1}},\ldots,s_{q_{b}}$ have been replaced by "1" and the superscripts $s_{q_{1}},\ldots,s_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$. \\
This is proved by induction. Indeed, for $L=1$ it is trivially true, by \eqref{S1-L1}. We assume that it is true for arbitrary $L\in \mathbb{N}$ and we prove that it holds for $L+1$. 
\begin{align*}
\left(S_{1}^{\otimes L}\right)^{-1}\otimes S_{1}^{-1}&=
\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}\right. \\&+\left. \sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}\right\}
\\&\otimes
\left\{ \sum_{s_{1}=1}^{N}e_{s_{L+1}}^{s_{L+1}}+(-1)\delta_{s_{L+1},1}\sum_{d_{L+1}=2}^{N}e_{1}^{d_{L+1}}\right\}
\\&=
\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L+1}=1}^{N}\left\{e_{s_{1},\ldots,s_{L+1}}^{s_{1},\ldots,s_{L+1}}\right. \\&+\left. \sum_{b=1}^{L+1}(-1)^{b}\sum_{q_{1}=1}^{L+1}\sum_{q_{2}=q_{1}+1}^{L+1}\ldots\sum_{q_{b}=q_{b-1}+1}^{L+1}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}\right\}
\end{align*}
\begin{comment}

@@

    \mathcal{L}^{rd}=\sum_{x,y\in\mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}^{rd}+\sum_{x\in V}\Gamma_{x}\mathcal{L}_{x}^{rd}

@@

	\mathcal{L}_{x}^{rd}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)

@@

\paragraph{Action on the occupation variable $n_{d}^{x}$ for the edge generator $\mathcal{L}_{x,y}^{rd}$}

@@

	\mathcal{L}_{x,y}n_{d}^{x}=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left((n_{d}^{x}-\delta_{a}^{x}+\delta_{b}^{x}+\delta_{a}^{y}-\delta_{b}^{y})-n_{d}^{x}\right)=\nu\left(n_{d}^{y}-n_{d}^{x}\right)
while for every $c\in \{2,\ldots,N\}$ we have 
\mathcal{L}_{x,y}^{c}n_{a}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left((n_{d}^{x}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(a)}^{y}-\delta_{b}^{y})-n_{\alpha}^{x}\right)=\sum_{a=1}^{N}n_{a}^{x}n_{q}^{y}-\sum_{\ell=1}^{N}n_{\alpha}^{x}n_{\ell}^{y}

@@

where we call $q\in \{2,\ldots,N\}$ such that $g_{i}(q)=\alpha$ and $\ell\in \{2,\ldots,N\}$ such that $g_{i}(\ell)\neq \alpha$.
	\mathcal{L}_{x,y}^{m}n_{d}^{x}=\sum_{a,b=2}^{N}n_{a}^{x}\left((n_{d}^{x}-\delta_{a}^{x}+\delta_{b}^{x})-n_{d}^{x}\right)=\sum_{b=1}^{N}(n_{b}^{x}-n_{d}^{x})
Then, summing over all indices $c\in\{2,\ldots,N\}\,:\,c\neq d$, we obtain \eqref{actionGraphRD}.
\paragraph{Action on the occupation variable $n_{d}^{x}$ for the site generator $\mathcal{L}_{x}^{rd}$}
Acting on $n_{d}^{x}$  with $\mathcal{L}_{x}^{rd}$ we obtain
	\mathcal{L}_{x}^{rd}n_{d}^{x}&=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left((n_{d}^{x}-\delta_{b}^{x}+\delta_{a}^{x})-n_{d}^{x}\right)=\alpha_{d}^{x}\sum_{b=1\,:\,b\neq d}^{N}n_{b}^{x}-n_{d}^{x}\sum_{b=1\,:b\neq d}^{N}\alpha_{b}^{x}
	\alpha_{d}^{x}\left(\nu-n_{d}^{x}\right)-n_{d}^{x}\left(\nu(\sigma_{11}+(N-1)\sigma_{12})-\alpha_{d}^{x}\right)
